---
title: "Raissa's reference document"
output: 
  html_document: default
  pdf_document: 
   fig_caption: yes 
   keep_tex: yes
   toc: yes
  bookdown::word_document2: default
  word_document: default
params:
  country1: 'Mauritius'
  country2: 'Canada'
---

```{r setup, include=FALSE, message = FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

My neighbour's name is Anna. She chose:

 * Mauritius
 * Canada
 
 1. Mauritius
 2. Canada


```{r tableChunk, eval=TRUE, message = FALSE}
library(gapminder)
library(dplyr)

df <- gapminder %>% filter(country %in% c('Poland','Canada')) 
knitr::kable(df)
```
```{r table2}
library(pander)
pander::pander(df,caption='A table with pander')
```


## Tip from Raissa
We are now going to make a table with the huxtable package. This is very helpful for conditional formatting specially when outputting to a word docume

```{r tableChunkHux, echo=TRUE, eval=TRUE, message=FALSE}
library(huxtable)
library(flextable)
dfHt <- huxtable(df,add_colnames = TRUE) 

condition <- which(dfHt$year>1990)
dfHt <- dfHt %>%  set_text_color(condition, everywhere,'blue') 

dfHt <- dfHt %>% set_all_borders(everywhere,everywhere,1) %>% set_all_border_colors(everywhere,everywhere,'green')

output_format <- knitr::opts_knit$get("rmarkdown.pandoc.to")
  if(('word_document' %in% output_format)|('docx' %in% output_format)){
huxtable::as_flextable(dfHt) } else {
  dfHt
}
```



## Plots

We are now going to create a plot for our two countries

```{r plot, echo=FALSE, fig.cap='Population of my two countries'}

plotData <- gapminder %>% filter(country %in% c('Mauritius','Canada'))

plotData %>% ggplot(aes(x=year,y=pop,color=country)) + geom_line()

```


## Using in-line code and parameter

Remember how we include parameters in our YAML header. I can now ask RMarkdown to include those names here. RMarkdown will print the first parameter if I put the inline code as follows:

  * `r params$country1`
  * `r params$country2`
  
  
## Using loops

```{r, results='asis'}
library(knitr)
library(pander)
out=NULL

for(ct in c(params$country1,params$country2)){
  env=new.env()
  print(ct)
  out = c(out,knit_expand('table_text.Rmd',envir=env))


}
```

You can put some text here before the tables


`r paste(knit(text = out), collapse = '\n\n')`